---
title: "Data Analysis"
author: "Nick Pangakis"
output: pdf_document
---

```{r setup, echo=FALSE, warning=F, message=F}
knitr::opts_chunk$set(echo = TRUE, fig.width=8, fig.height=4,include=F,eval=TRUE,results = F,warning=F,message=F,echo=FALSE)
options(scipen=9999)
if(!require('pacman')) {
  install.packages('pacman')
}
pacman::p_load(ltm, tidyverse, car) 
```

## Overview

This .Rmd involves the data analysis for the experimental data.

```{r Load in data}
# Load in data (data is available upon request)
data <- read_csv("data_clean.csv") %>% 
  mutate(condition = as.factor(condition),
         starvation_threat = as.factor(starvation_threat),
         persecution_threat = as.factor(persecution_threat))
```

```{r Minor Experimental Assessments}
# Check length of survey - 4.7 minutes
median(data$Duration__in_seconds_)/60

##### Check reliability of survey batteries
#DV1: Attitudes toward Hypothetical Family of Migrants - .895 good
data %>% 
  select(DV1_Q1_1,
         DV1_Q1_2,
         DV1_Q1_3,
         DV1_Q1_4) %>% 
  cronbach.alpha()


#DV2: Immigration Policy Attitudes - .818 good
data %>% 
  select(DV2_Q2_1,
         DV2_Q2_2,
         DV2_Q2_3,
         DV2_Q2_4) %>% 
  cronbach.alpha()

#dv3: Voluntariness - .832 good
data %>% 
  select(DV3_Q4_1,
         DV3_Q4_2) %>% 
  cronbach.alpha()

#dv3: Attribution of Responsibility - .728 somewhat low
data %>% 
  select(responsibleA,
         responsibleB) %>% 
  cronbach.alpha()

```

## Manipulation Checks:

Manipulation checks were included at the end of the survey after measuring the dependent variables. To check whether reason for migration was successfully manipulated, respondents were asked why the Lina family tried to come to the United States. Respondents were encouraged to select all options that applied, and the options ranged from (a) economic opportunity, (b) avoid starvation, (c) avoid persecution and violence, and (d) unsure.

### Economic Reasons for Migrating

```{r}
econ_mc <- lm(MC_economic ~ starvation_threat*persecution_threat,
             data=data)
# Regression results
summary(econ_mc)
# Anova results
Anova(mod=econ_mc)
```


```{r,include = T, results=T}
# Economic
means_starv <- data %>%
  group_by(starvation_threat) %>%
  rename(var = starvation_threat) %>% 
  dplyr::summarize(mean = mean(MC_economic))

means_starv$factor <- "Starvation Threat"

means_pers <- data %>%
  group_by(persecution_threat) %>%
  rename(var = persecution_threat) %>% 
  dplyr::summarize(mean = mean(MC_economic))

means_pers$factor <- "Violence Threat"

means <- rbind(means_starv,means_pers)
means$factor <- as.factor(means$factor)
means <- means %>% 
  mutate(var = case_when(var == 0 ~ "Absence of Factor", TRUE ~ "Presence of Factor"))

ggplot(means,aes(x=var,y=mean)) + geom_point() + 
  geom_line(group = 1) +
  facet_wrap(~factor) +
    labs(title="Manipulation Check: Economic Opportunity as Reason for Migrating",y="Percent of Respondents",x="Reason for Migrating") + 
  theme(plot.title = element_text(hjust=0.5),
        text = element_text(size=10)) +
  scale_y_continuous(labels = scales::percent)

```

The above plot shows the percentage of respondent's who selected that the Lina family traveled to the United States for "economic opportunity." Although respondents exposed to starvation threat were more likely to say that the Lina family traveled to the US for economic opportunity, the main effect of the starvation threat factor is not significant (F = 2.55, p = .111). Likewise, the main effect of persecution threat is also not significant (F = 2.49, p = .115). That being said, there is a significant interaction between starvation and persecution threat (F = 7.68, p = .006). As a whole, this is suggestive evidence that respondents interpreted starvation threat as reason for migrating as similar to economic opportunity. 

### Starvation as Reason for Migrating

```{r}
starv_mc <- lm(MC_starvation ~ starvation_threat*persecution_threat,
             data=data)
# Regression results
summary(starv_mc)
# Anova results
Anova(mod=starv_mc)
```

```{r,include = T, results=T}
# Starvation

means_starv <- data %>%
  group_by(starvation_threat) %>%
  rename(var = starvation_threat) %>% 
  dplyr::summarize(mean = mean(MC_starvation))

means_starv$factor <- "Starvation Threat"

means_pers <- data %>%
  group_by(persecution_threat) %>%
  rename(var = persecution_threat) %>% 
  dplyr::summarize(mean = mean(MC_starvation))

means_pers$factor <- "Violence Threat"

means <- rbind(means_starv,means_pers)
means$factor <- as.factor(means$factor)
means <- means %>% 
  mutate(var = case_when(var == 0 ~ "Absence of Factor", TRUE ~ "Presence of Factor"))

ggplot(means,aes(x=var,y=mean)) + geom_point() + 
  geom_line(group = 1) +
  facet_wrap(~factor) +
    labs(title="Manipulation Check: Avoid Starvation as Reason for Migrating",y="Percent of Respondents",x="Reason for Migrating") + 
  theme(plot.title = element_text(hjust=0.5),
        text = element_text(size=10)) +
  scale_y_continuous(labels = scales::percent)
```

The above plot shows the percentage of respondent's who selected that the Lina family traveled to the United States to "avoid starvation." The main effect of the starvation threat factor is highly significant (F = 106.55, p = <.0001). None of the other factors are significant.

### Avoid Violence as Reason for Migrating

```{r}
pers_mc <- lm(MC_persecution ~ starvation_threat*persecution_threat,
             data=data)
# Regression results
summary(pers_mc)
# Anova results
Anova(mod=pers_mc)
```

```{r,include = T, results=T}
# Violence

means_starv <- data %>%
  group_by(starvation_threat) %>%
  rename(var = starvation_threat) %>% 
  dplyr::summarize(mean = mean(MC_persecution))

means_starv$factor <- "Starvation Threat"

means_pers <- data %>%
  group_by(persecution_threat) %>%
  rename(var = persecution_threat) %>% 
  dplyr::summarize(mean = mean(MC_persecution))

means_pers$factor <- "Violence Threat"

means <- rbind(means_starv,means_pers)
means$factor <- as.factor(means$factor)
means <- means %>% 
  mutate(var = case_when(var == 0 ~ "Absence of Factor", TRUE ~ "Presence of Factor"))

ggplot(means,aes(x=var,y=mean)) + geom_point() + 
  geom_line(group = 1) +
  facet_wrap(~factor) +
    labs(title="Manipulation Check: Avoid Violence as Reason for Migrating",y="Percent of Respondents",x="Reason for Migrating") + 
  theme(plot.title = element_text(hjust=0.5),
        text = element_text(size=10)) +
  scale_y_continuous(labels = scales::percent)
```

The above plot shows the percentage of respondent's who selected that the Lina family traveled to the United States to "avoid persecution and violence". The main effect of the persecution threat factor is highly significant (F = 53.05, p = <.0001). None of the other factors are significant.

### Unsure Reason for Migrating

```{r}
unsure_mc <- lm(MC_unsure ~ starvation_threat*persecution_threat,
             data=data)
# Regression results
summary(unsure_mc)
# Anova results
Anova(mod=unsure_mc)
```


```{r,include = T, results=T}
# Unsure
means_starv <- data %>%
  group_by(starvation_threat) %>%
  rename(var = starvation_threat) %>% 
  dplyr::summarize(mean = mean(MC_unsure))

means_starv$factor <- "Starvation Threat"

means_pers <- data %>%
  group_by(persecution_threat) %>%
  rename(var = persecution_threat) %>% 
  dplyr::summarize(mean = mean(MC_unsure))

means_pers$factor <- "Violence Threat"

means <- rbind(means_starv,means_pers)
means$factor <- as.factor(means$factor)
means <- means %>% 
  mutate(var = case_when(var == 0 ~ "Absence of Factor", TRUE ~ "Presence of Factor"))

ggplot(means,aes(x=var,y=mean)) + geom_point() + 
  geom_line(group = 1) +
  facet_wrap(~factor) +
    labs(title="Manipulation Check: Unsure Reason for Migrating",y="Percent of Respondents",x="Reason for Migrating") + 
  theme(plot.title = element_text(hjust=0.5),
        text = element_text(size=10)) +
  scale_y_continuous(labels = scales::percent)
```

The above plot shows the percentage of respondent's who selected that the were "unsure" why the Lina family traveled to the United States. The main effect of the starvation threat factor is significant (F = 15.41, p = <.001) and so is the main effect for persecution threat factor (F = 3.19, p = <.075). Respondents exposed to either or both of the factors were less likely to say they were unsure why the migrant family was travelling to the country. 

## Analysis of Main Results

### Attitudes Toward Hypothetical Immigrant Family

```{r}
# DV1
dv_family_model <- lm(DV1_family ~ starvation_threat*persecution_threat + republican + education,
             data=data)
# Regression results
summary(dv_family_model)
# Anova results
Anova(mod=dv_family_model)

# DV1 - log
dv_family_model_log <- lm(log(DV1_family) ~ starvation_threat*persecution_threat + republican + education,
                          data=data)
# Regression results
summary(dv_family_model_log)
```

```{r,include = T, results=T}
means_starv <- data %>%
  group_by(starvation_threat) %>%
  rename(var = starvation_threat) %>% 
  dplyr::summarize(mean = mean(DV1_family))

means_starv$factor <- "Starvation Threat"

means_pers <- data %>%
  group_by(persecution_threat) %>%
  rename(var = persecution_threat) %>% 
  dplyr::summarize(mean = mean(DV1_family))

means_pers$factor <- "Violence Threat"

means <- rbind(means_starv,means_pers)
means$factor <- as.factor(means$factor)
means <- means %>% 
  mutate(var = case_when(var == 0 ~ "Absence of Factor", TRUE ~ "Presence of Factor"))

ggplot(means,aes(x=var,y=mean)) + geom_point() + 
  geom_line(group = 1) +
  facet_wrap(~factor) +
    labs(title="Effects of a Migrant's Reason for Migrating on Native Immigration Attitudes",
         y="Immigration Support",x="Reason for Migrating") + 
  theme(plot.title = element_text(hjust=0.5),
        text = element_text(size=10))
```

The above plot shows that native's immigration attitudes are more favorable when migrants are experiencing a threat in their home country. Including education and partisanship as covariates, a 2 by 2 ANOVA reveals that the mean support for the hypothetical family of migrants was different across the presence and absence of starvation threat as a reason for migration (F = 3.95, p = .048). Because there are only two levels to the starvation threat factor and subjects reported higher mean support for the Lina family when exposed to starvation threat (3.45) than no starvation threat (3.19), I conclude that starvation threat caused a notable favorable shift in immigration attitudes. Specifically, starvation threat improved immigration attitudes by 13.7 percentage points, which is around one-third of the size of being a Republican (34.7 percent decrease).

Thus, when the threats and risks associated with staying in one’s country are equalized, natives do not penalize migrants who leave their country for economic reasons relative to migrants immigrating due to fear of violence. When the consequences are dire, economic migrants are viewed just as favorably as migrants experiencing violent threats in their home country. In fact, the 2 by 2 ANOVA revealed no significant difference across the presence and absence of violence threat as a reason for migration (F = .0001, p = .994), which possibly suggests that natives are more sympathetic to starvation as a reason for migrating than violent persecution.

### Attitudes Toward Immigration Policy 

```{r}
# DV2
dv_policy_model <- lm(DV2_policy ~ starvation_threat*persecution_threat 
                      + republican + education,
                      data=data)
# Regression results
summary(dv_policy_model)
# Anova results
Anova(mod=dv_policy_model)

# DV2 - log
dv_policy_model_log <- lm(log(DV2_policy) ~ starvation_threat*persecution_threat 
                          + republican + education,
                          data=data)
# Regression results
summary(dv_policy_model_log)
```

Results for policy attitudes: positive effect of both factors on policy attitudes. However, neither effect is significant.

### Voluntariness

```{r}
# DV3a - voluntariness
dv_voluntary_model <- lm(DV3a_voluntary ~ starvation_threat*persecution_threat 
                      + republican + education,
                      data=data)
# Regression results
summary(dv_voluntary_model)
# Anova results
Anova(mod=dv_voluntary_model)

# log
dv_voluntary_model_log <- lm(log(DV3a_voluntary) ~ starvation_threat*persecution_threat 
                          + republican + education,
                          data=data)
# Regression results
summary(dv_voluntary_model_log)
```

Results for attitudes around voluntariness: positive effect of both factors on attitudes and both are significant.

### Attributions of Responsibility

```{r}
# DV3b - Responsibility
### Do separately because low Cronbach's Alpha

# First question
dv_respon_model_1 <- lm(responsibleA ~ starvation_threat*persecution_threat 
                      + republican + education,
                      data=data)
# Regression results
summary(dv_respon_model_1)
# Anova results
Anova(mod=dv_respon_model_1)

# log
dv_respon_model_1_log <- lm(log(responsibleA) ~ starvation_threat*persecution_threat 
                          + republican + education,
                          data=data)
# Regression results
summary(dv_respon_model_1_log)

# Second question
dv_respon_model_2 <- lm(responsibleB ~ starvation_threat*persecution_threat 
                      + republican + education,
                      data=data)
# Regression results
summary(dv_respon_model_2)
# Anova results
Anova(mod=dv_respon_model_2)

# log
dv_respon_model_2_log <- lm(log(responsibleB) ~ starvation_threat*persecution_threat 
                          + republican + education,
                          data=data)
# Regression results
summary(dv_respon_model_2_log)
```

Results for attitudes around attributions of responsibility: positive effect of both factors on attitudes and both are significant.
